\documentclass[bibtotoc,liststotoc]{scrbook}
\usepackage[utf8]{inputenc}
\usepackage[draft]{fixme}
\begin{document}
\title{The SU4SML Manual}
\author{Achim Brucker and Jürgen Doser}
\maketitle

\tableofcontents
\chapter{Introduction}

general introduction and overview over the capabilities presented
below. Installation and ``getting started'' and short usage
instructions?  

Overview of the use of su4sml in the complete toolchain as described
in \cite{brucker.ea:mda:2006-b}.  Also mention the work in
\cite{marcel.beer:sa:2006,beer:generic:2007,brucker.ea:mda:2006-b}.
 
\chapter{XMI \& Rep Parser}

describe requirements on the xmi format. How to adjust to other xmi
dialects. How to add other input languages (other than xmi) to the
rep\_parser. 

\chapter{Model Transformation Support}

describe any major transformation function (su2holocl, normalizing
associations,...), as well as any major functionality for writing
transformation functions (are there any?)  

\section{su2holocl}

Based on \cite{crijke:transforming:2006}.

\section{association-related}

\section{generic transformation framework?}

\chapter{The HOL-OCL Interface?}

describe any requirements/limitations the HOL-OCL interface currently
has. (no associations, etc.). Based on
\cite{brucker.ea:hol-ocl-book:2006}? 

\chapter{The Generic Code Generator: GCG}

\section{The GCG Framework}

some overall architecture stuff from
\cite{eidenbenz:development:2006}. lots of 
pictures :)  

\section{Individual Cartridge Documentation}

describe each cartridge in a fixed form (using some predefined
makros). Basically a list of the supported variables, lists, and
predicates of the cartridge, together with (short) descriptions of
them. 

\subsection{The BaseCartridge}

\subsection{The C\# Cartridge}

\subsection{The StateMachine Cartridge}
Based on \cite{adelsberger:development:2006}

\subsection{The JavaCartridge}

\subsection{The Junit Cartridge}

Based on \cite{stock:automatic:2007}

\subsection{The SecureUML Cartridge}

\subsection{...}
 
\section{Misc. utilities}

 subsections for additional things like the jtestdataaccessor
  library from Manfred, or the statemachine animator from Rolf.

\chapter{Developer's Guide}
\section{Build Setup}
We currently support the following SML compiler:
\begin{itemize}
\item sml/NJ (tested with version 110.52 and 110.62) using CM files
\item mlton  (tested with version 20061107-1) using CM files
\item poly/ML (tested with version 5.0) using ROOT.ML files (i.e., plain \texttt{use} commands)
\end{itemize}


%%% bibliography: all the related papers and student theses
\bibliographystyle{alpha}
\bibliography{su4sml}
%\appendix
%\listoffixmes
\end{document}
